A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2023-11-26 pilot-publication/manuscript.Rmd

- Recruitment rate. For both patients and residents this was equal to
  the proportion of participants enrolled, out of the total number of
  eligible participants, over the course of the pilot study.
- Lost to follow up rate. This applied only to patients and was equal
  to the proportion of patients that do not complete 30 day follow up,
  out of all enrolled patients, over the course of the pilot study.
- Pass rate. This applied only to residents in the intervention
  arms and equal the proportion of residents that pass the training
  programme, out of the total number of trained residents, over the
  course of the pilot study.
- Missing data rate. This applied to each outcome and variable and was
  equal to the proportion of missing data, over the course of the
  pilot study.
- Differences in distributions of observed and extracted data. This
  applied to each outcome and variable and compared the distributions
  of data collected by observations versus extracted from hospital
  records. For quantitative variables this was be the difference in
  means, standard deviations, medians, interquartile ranges, and
  ranges. For qualitative variables this was the differences in
  absolute counts and percentages, across categories.

>>>>

- Recruitment rate. For both patients and residents this was equal to
  the proportion of participants enrolled, out of the total number of
  eligible participants, over the course of the pilot study.
- Lost to follow up rate. This applied only to patients and was equal
  to the proportion of patients that did not complete 30 day follow up,
  out of all enrolled patients, over the course of the pilot study.
- Pass rate. This applied only to residents in the intervention
  arms and equal the proportion of residents that pass the training
  programme, out of the total number of trained residents, over the
  course of the pilot study.
- Missing data rate. This applied to each outcome and variable and was
  equal to the proportion of missing data, over the course of the
  pilot study.
- Differences in distributions of observed and extracted data. This
  applied to each outcome and variable and compared the distributions
  of data collected by observations versus extracted from hospital
  records. For quantitative variables this was be the difference in
  means, standard deviations, medians, interquartile ranges, and
  ranges. For qualitative variables this was the differences in
  absolute counts and percentages, across categories.
